**NAME OF THIS STUDY**

### 2018-11-06 submission/manuscript.Rmd
styling

```{r model_parameters, echo=FALSE, results='asis'}
model_param <- read.table('../data/process/model_parameters.txt', header=T, sep='\t')
kable(model_param, caption = "Table 1 Parameters and software implementation of the classification algorithms") %>%
  kable_styling("striped", full_width = F)
```
\vspace{35mm}

>>>>

```{r model_parameters, echo=FALSE, results='asis'}
model_param <- read.table('../data/process/model_parameters.txt', header=T, sep='\t') %>% 
  select(-Value)
kable(model_param, caption = "Table 1 Parameters and software implementation of the classification algorithms") %>%
  kable_styling("striped", full_width = F, font_size=10)
```
\vspace{35mm}
